{ \fontfamily{ptm}\selectfont First Order Nonsmooth Optimization: Algorithm Design, Variational analysis, and Applications }

### 2025-01-01 Notebook LaTEX/Proposal/main.tex
>w<, changes

    \subsection{Method Free R-WAPG}\label{sec:spectral-momentum}
        \todoinline{
            Algorithm, and results of numerical experiments with their descriptions. 
        }
        This section introduces an algorithm of our creation inspired by the remark of Proposition \ref{prop:stepwise-lyapunov}. 
        Algorithm \ref{alg:free-rwapg} estimates the $\mu$ constant as the algorithm executes and pools the information using the Bregman Divergence of the smooth part function $f$. 
        \begin{algorithm}
            \begin{algorithmic}[1]
            {\footnotesize
            \STATE{\textbf{Input: } $f, g, x_0, L > \mu \ge 0, \in \RR^n, N \in \N$}
            \STATE{\textbf{Initialize: }$y_0 := x_0;L := 1; \mu := 1/2; \alpha_0 = 1;$}
            \STATE{\textbf{Compute: } $f(y_k)$; }
            \FOR{$k = 0, 1, 2, \cdots, N$}
                \STATE{\textbf{Compute: }$\nabla f(y_k); x^+:= [I + L^{-1}\partial g](y_k - L^{-1}\nabla f(y_k))$;}
                \WHILE{$L/2\Vert x^+ - y\Vert^2 < D_f(x^+, y)$}
                    \STATE{$L:= 2L$;}
                    \STATE{$x^+ = [I + L^{-1}\partial g](y_k - L^{-1}\nabla f(y_k))$; }
                \ENDWHILE
                \STATE{$x_{k + 1} := x^+$;}
                \STATE{$\alpha_{k + 1} := (1/2)\left(\mu/L - \alpha_{k}^2 + \sqrt{(\mu/L - \alpha_{k}^2)^2 + 4\alpha_{k}^2}\right)$;}
                \STATE{$\theta_{k + 1} := \alpha_k(1 - \alpha_k)/(\alpha_k^2 + \alpha_{k + 1})$;}
                \STATE{$y_{k + 1}:= x_{k + 1} + \theta_{k + 1}(x_{k + 1} - x_k)$; }
                \STATE{\textbf{Compute: } $f(y_{k + 1})$}
                \STATE{$\mu := (1/2)(2D_f(y_{k + 1}, y_{k})/\Vert y_{k + 1} - y_k\Vert^2) + (1/2)\mu$;}
            \ENDFOR
            }
            \end{algorithmic}
            \caption{Free R-WAPG}
            \label{alg:free-rwapg}
        \end{algorithm}
        \par
        Line 5-8 estimates upper bound for the Lipschitz constant and find $x^+$, the next iterates produced by proximal gradient descent on previous $y_k$.
        Line 9 updates $x_{k + 1}$ to be $x^+$, a successful iterate identified by the Lipschitz line search routine. 
        Line 10 updates the R-WAPG sequence $\alpha_k$ for the iterates $y_{k + 1}$. 
        Line 13 updates $\mu$ using the Bregman Divergence of $f$ from iterates $y_{k + 1}, y_k$. 
        \par
        Assume $L$ given is an upper bound of the Lipschitz smoothness constant of $f$, then the algorithm calls $f(\cdot)$ two times, and $\nabla f(\cdot)$ once per iteration. 
        The algorithm computes $\nabla f(y_k)$ once for $x^+$, $f(y_{k + 1})$ once for Bregman Divergence because $f(y_{k})$ is evaluated from the previous iteration, and $f(x^+)$ once for Lipschitz constant line search condition. 
        We note that $f(y_0)$ is computed before the start of the for loop. 
        And finally, it evaluates proximal of $g$ at $y_k - L^{-1}\nabla f(y_k)$ once. 
    \subsection{Free R-WAPG numerical experiments}
        \subsubsection{Simple regression}
        \subsubsection{LASSO}

\section{Catalyst accelerations and future works}\label{sec:catalyst}
    \todoinline{\noindent
        Literatures review of the topics in Catalyst acceleration method. 
        Here is a list of topics: 
        \begin{enumerate}
            \item The original accelerated PPM. 
            \item The Catalyst with weakly convex objectives. 
        \end{enumerate}
        After the literature reviews of the core literatures, move on and state new research directions and open problems. 
        There are several directions for open problem: 
        \begin{enumerate}
            \item APPM method for monotone operators instead of just subgradient, whether the same framework exists in a greater context. 
            \item Accelerated Proximal Bregman Method. 
            \item Removing smoothness assumption in Catalyst acceleration framework. 
        \end{enumerate}  
    }
    \todoinline{\noindent
        A list of relevant literatures: 
        \begin{enumerate}
            \item Güler's 1992 paper on Accelerated Proximal Point method. 
            \item Lin's, and Payquette's three trilogy paper on Catalyst acceleration for convex, non-convex Variance reduced algorithm. 
        \end{enumerate}
    }

>>>>

    \subsection{Free R-WAPG}\label{sec:spectral-momentum}
        This section introduces an algorithm of our creation inspired by the remark of Proposition \ref{prop:stepwise-lyapunov}. 
        Algorithm \ref{alg:free-rwapg} estimates the $\mu$ constant as the algorithm executes and pools the information using the Bregman Divergence of the smooth part function $f$. 
        \begin{algorithm}
            \begin{algorithmic}[1]
            {\footnotesize
            \STATE{\textbf{Input: } $f, g, x_0, L > \mu \ge 0, \in \RR^n, N \in \N$}
            \STATE{\textbf{Initialize: }$y_0 := x_0;L := 1; \mu := 1/2; \alpha_0 = 1;$}
            \STATE{\textbf{Compute: } $f(y_k)$; }
            \FOR{$k = 0, 1, 2, \cdots, N$}
                \STATE{\textbf{Compute: }$\nabla f(y_k); x^+:= [I + L^{-1}\partial g](y_k - L^{-1}\nabla f(y_k))$;}
                \WHILE{$L/2\Vert x^+ - y\Vert^2 < D_f(x^+, y)$}
                    \STATE{$L:= 2L$;}
                    \STATE{$x^+ = [I + L^{-1}\partial g](y_k - L^{-1}\nabla f(y_k))$; }
                \ENDWHILE
                \STATE{$x_{k + 1} := x^+$;}
                \STATE{$\alpha_{k + 1} := (1/2)\left(\mu/L - \alpha_{k}^2 + \sqrt{(\mu/L - \alpha_{k}^2)^2 + 4\alpha_{k}^2}\right)$;}
                \STATE{$\theta_{k + 1} := \alpha_k(1 - \alpha_k)/(\alpha_k^2 + \alpha_{k + 1})$;}
                \STATE{$y_{k + 1}:= x_{k + 1} + \theta_{k + 1}(x_{k + 1} - x_k)$; }
                \STATE{\textbf{Compute: } $f(y_{k + 1})$}
                \STATE{$\mu := (1/2)(2D_f(y_{k + 1}, y_{k})/\Vert y_{k + 1} - y_k\Vert^2) + (1/2)\mu$;}
            \ENDFOR
            }
            \end{algorithmic}
            \caption{Free R-WAPG}
            \label{alg:free-rwapg}
        \end{algorithm}
        \par
        Line 5-8 estimates upper bound for the Lipschitz constant and find $x^+$, the next iterates produced by proximal gradient descent on previous $y_k$.
        Line 9 updates $x_{k + 1}$ to be $x^+$, a successful iterate identified by the Lipschitz line search routine. 
        Line 10 updates the R-WAPG sequence $\alpha_k$ for the iterates $y_{k + 1}$. 
        Line 13 updates $\mu$ using the Bregman Divergence of $f$ from iterates $y_{k + 1}, y_k$. 
        \par
        Assume $L$ given is an upper bound of the Lipschitz smoothness constant of $f$, then the algorithm calls $f(\cdot)$ two times, and $\nabla f(\cdot)$ once per iteration. 
        The algorithm computes $\nabla f(y_k)$ once for $x^+$, $f(y_{k + 1})$ once for Bregman Divergence because $f(y_{k})$ is evaluated from the previous iteration, and $f(x^+)$ once for Lipschitz constant line search condition. 
        We note that $f(y_0)$ is computed before the start of the for loop. 
        And finally, it evaluates proximal of $g$ at $y_k - L^{-1}\nabla f(y_k)$ once. 
    \subsection{Free R-WAPG numerical experiments}
        \subsubsection{Simple regression}
        \subsubsection{LASSO}

\section{Catalyst accelerations and future works}\label{sec:catalyst}
    \todoinline{\noindent
        Literatures review of the topics in Catalyst acceleration method. 
        Here is a list of topics: 
        \begin{enumerate}
            \item The original accelerated PPM. 
            \item The Catalyst with weakly convex objectives. 
        \end{enumerate}
        After the literature reviews of the core literatures, move on and state new research directions and open problems. 
        There are several directions for open problem: 
        \begin{enumerate}
            \item APPM method for monotone operators instead of just subgradient, whether the same framework exists in a greater context. 
            \item Accelerated Proximal Bregman Method. 
            \item Removing smoothness assumption in Catalyst acceleration framework. 
        \end{enumerate}  
    }
    \todoinline{\noindent
        A list of relevant literatures: 
        \begin{enumerate}
            \item Güler's 1992 paper on Accelerated Proximal Point method. 
            \item Lin's, and Payquette's three trilogy paper on Catalyst acceleration for convex, non-convex Variance reduced algorithm. 
        \end{enumerate}
    }
    In this section, we assume that $F: \RR^n \rightarrow \overline \RR$ is a convex function. 
    This section reports major results from literatures concerning the mthod of Catalyst Acceleration.

    \subsection{Lin's original Catalyst}

    \subsection{Catalyst Adapted to Non-convexity}
